Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.

### 2018-12-04 paper/snakemajoranas.tex
improve spectrum algo text

%%██████████████████████████████████████████████████████████████████████████
%%██ Analytical estimate
%%██████████████████████████████████████████████████████████████████████████
\section{Analytical estimate}
We claim that the hardening of the gap is due to the cutoff of long trajectories. 
In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
We then compute the scattering matrix to find the Andreev bound spectrum as a function of the momentum along the strip direction.
We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.

@@

Where $\lambda$ are the eigenvalues of $A$.
Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)$, and since $\alpha$ is unitary and only defined in the postitive imagionary plane, $E_{i}=\textrm{real}\left(\pm\sqrt{1/\lambda_{i}}\right)$.  % TODO: add the mathematical notation for taking the lambda.imag > 0.
Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Analytical estimate
%%██████████████████████████████████████████████████████████████████████████
\section{Analytical estimate}
We claim that the hardening of the gap is due to the cutoff of long trajectories. 
In order to verify this is the case, we take a ribbon SNS junction with magnetic field rotated such that it corresponds to a rising section of the zigzag.
We then compute the scattering matrix [Eq.~\eqref{eq:smatrix}] to find the Andreev bound spectrum as a function of the momentum along the strip direction.
We cut off the spectrum at the momentum corresponding to the proposed cutoff in the zigzag, and compare it to the numerically obtained gap for a true zigzag system.

@@

Where $\lambda_i$ are the eigenvalues of $A$.
Inverting $\alpha\left(E\right)\equiv\exp\left(-i\arccos\left(E/\Delta\right)\right)$ gives $\frac{E}{\Delta}=\frac{\alpha^{2}+1}{2\alpha}=\frac{1}{2}\left(\alpha+\alpha^{-1}\right)=\textrm{Re}(\alpha)$, where the last equality holds because $\alpha$ is unitary.
Then, since $\alpha$ is only defined in the postitive imagionary plane, the energies are $\frac{E_{i}}{\Delta}=\textrm{Re}\left(\sqrt{-1/\lambda_{i}}\right)$ where we take the root which has a postitive imagionary part.
Using this result and Eq.~\eqref{eq:smatrix}, we numerically find the Andreev spectrum.
